---
title: "Question 3"
---

```{r, message = FALSE}
library(tidyverse)
```

##### (a) Write a function factory `moment` which returns a function to compute the $k$ raw moment of a input ($k$ positive integer).

Hint: a $k$ raw moment of a vector `x` could be computed by `mean(x^k)`


```{r}
# YOUR definition of moment here
moment <- function(k){
  function(x) {
    mean(x ^ k)
  }
}
```


```{r}
x <- rnorm(10)

m1 <- moment(1)
m1(x)  # it should equal mean(x)

m2 <- moment(2)
m2(x)  # it should equal mean(x^2)
```



##### (b) Consider the `mpg` dataset and compute the first to fifth moments for each numerical column. Create a data frame where the columns are the variables and the rows are the moments. Print the data frame for visualization.


Hint: There are several solutions, the easiest one may be `map_dfr` or `map_dfc`. Another alternative is
`cross`/`map`/`reduce`.

```{r}
data(mpg)
nums <- unlist(lapply(mpg, is.numeric)) 
data <- mpg[ , nums]
head(data, 5)
```

```{r}
d <- map(1:5, moment)
first <- map(list(data$displ, data$year, data$cyl, data$cty, data$hwy), d[1])
second <- map(list(data$displ, data$year, data$cyl, data$cty, data$hwy), d[2])
third <- map(list(data$displ, data$year, data$cyl, data$cty, data$hwy), d[3])
fourth <- map(list(data$displ, data$year, data$cyl, data$cty, data$hwy), d[4])
fifth <- map(list(data$displ, data$year, data$cyl, data$cty, data$hwy), d[5])

df <- as.data.frame(do.call(cbind, first))
colnames(df)<- c("displ", "year", "cyl", "cty", "hwy")
df <- rbind(df, second)
df <- rbind(df, third)
df <- rbind(df, fourth)
df <- rbind(df, fifth)
head(df, 5)
```